DATA 621 Homework #4

### 2019-11-15 hw4/HW4_Mike.Rmd
More tinkering

```{r}
amt_fit <- lm(TARGET_AMT ~ BLUEBOOK, amt_train)
summary(amt_fit)
```

>>>>

```{r}
rural_fit <- train %>%
  filter(TARGET_FLAG == 1) %>%
  filter(URBAN_DRIVER == 0) %>%
  lm(TARGET_AMT ~ BLUEBOOK + CAR_AGE + TRAVTIME, .)
urban_fit <- train %>%
  filter(TARGET_FLAG == 1) %>%
  filter(URBAN_DRIVER == 1) %>%
  lm(TARGET_AMT ~ BLUEBOOK, .)
summary(urban_fit)
```

```{r}
M <- train %>%
  filter(TARGET_FLAG == 1) %>%
  filter(URBAN_DRIVER == 1) %>%
  purrr::keep(is.numeric) %>%
  na.omit() %>%
  cor(.)
corrplot(M, type = "upper")
```

```{r}
evaluation$TARGET_FLAG <- ifelse(predict.glm(model, evaluation, "response") >= 0.5, 1, 0)
# We assume that everyone with a TARGET_FLAG = 0 has a TARGET_AMT as zero.  
# Urban drivers will use one model, rural another
evaluation$urban_yhat <- predict(urban_fit, evaluation)
evaluation$rural_yhat <- predict(rural_fit, evaluation)
evaluation <- evaluation %>%
  mutate(TARGET_AMT = ifelse(URBAN_DRIVER == 1, urban_yhat, rural_yhat)) %>%
  mutate(TARGET_AMT = ifelse(TARGET_FLAG == 0, 0, TARGET_AMT))
```
